Downstream analysis: A pipeline to analyse time-course gene expression data

### 2019-05-01 scripts/04_downstream_analysis.Rmd
Changes to downstream analysis

Once the gene ID to GO mapping list is created, `moanin` provides a simple
interface to `topGO` to fetch enriched GO terms.

```{r go_term_enrichment, results="hide", message=FALSE}

scores = as.numeric(labels == cluster)
names(scores) = gene_names
go_terms_enriched = find_enriched_go_terms(
    scores,
    gene_id_go_mapping, ontology="BP")

>>>>

Once the gene ID to GO mapping list is created, `moanin` provides a simple
interface to `topGO` to fetch enriched GO terms. Here, we show an example of
running a GO term enrichment on the "Biological process" ontology (BP).

```{r go_term_enrichment, results="hide", message=FALSE}
scores = as.numeric(labels == cluster)
names(scores) = gene_names
go_terms_enriched = find_enriched_go_terms(
    scores,
    gene_id_go_mapping, ontology="BP")
```
